### 2019-08-08 paper/paper.tex
codes for ensembles

@@

%\begin{verbatim}
%\bibliographystyle{juliacon}
%\bibliography{ref}
%\end{verbatim}
%When submitting the document source (.tex) file to external
%parties, the ref.bib file should be sent with it.
%\cite{bezanson2017julia}

>>>>

\vskip 6pt

@@

Setup pipeline for training and prediction:
\begin{lstlisting}[language = Julia]
@everywhere function predict(learner,
            data,train_ind,test_ind)

  features = convert(Matrix,data[:, 1:(end-1)])
  labels = convert(Array,data[:, end])
  # Create pipeline
  pipeline = Pipeline(
    Dict(
      :transformers => [
        OneHotEncoder(), # nominal to bits
        Imputer(), # Imputes NA values
        StandardScaler(), # normalize
        learner # Predicts labels on instances
      ]
    )
  )

  # Train
  fit!(pipeline, features[train_ind, :],
       labels[train_ind])

  # Predict
  predictions = transform!(pipeline, 
      features[test_ind, :])

  # Assess predictions
  result = score(:accuracy, 
      labels[test_ind], predictions)
  return result
end
\end{lstlisting}

TODO: 
\begin{itemize}
\item add plots
\item add stats output
\item add more examples from docs
\end{itemize}
%\begin{verbatim}
%\bibliographystyle{juliacon}
%\bibliography{ref}
%\end{verbatim}
%When submitting the document source (.tex) file to external
%parties, the ref.bib file should be sent with it.
%\cite{bezanson2017julia}
